---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
load("data_maryland.RData")
# m1 <- glm(y[,1]~x[,1],family=poisson(link = 'log')) # model for Allegany
```
Here, we are making an assumption that an outbreak is occurred only when it's larger than 86% quantile value of the positive cases for each location. We may consider using the ratio of no.case over population, but in real-life scenario, the population could get quite mobile from time to time, which makes the estimation of population for each city less reliable. 


EDA
```{r}
raw_plot <- function(city_index,data){
  plot(data[,city_index],type = 'l', main = paste('Covid cases in',colnames(data)[city_index]),xlab='Time(in days)',ylab='Number of cases')
  abline(h = mean(data[,city_index]), col="red" )
}

par(mfrow=c(3,3))
for (i in 1:9){ # plot first 9 counties
  raw_plot(i+2,data)
}
```


MCMC
```{r}
load("trials_mcmc/maryland/maryland_ln(0.52)_ln(4.36).RData")
sigma <- cov(chain[-1,c(1,2)])
Sigma <- (2.38^2/dim(sigma)[1])*sigma

mvrnorm(n=1,mu=c(0, 0),Sigma=Sigma)
```


















```{r}
##### Values for simulation
N <- nrow

##### now prepare dat for JAGS
## N is the number of entries
## y is the outcome in the data
## V is the variance in the data
dat <- list("N" = N, "y" = data$Allegany, "V" = data_x$Allegany+1)  # names list of numbers

##### Initial values
inits <- list( d = 0.0 )

require(rjags)
require(coda)
```



### JAGS

```{r}
# set up a model in BUGS (https://rstudio-pubs-static.s3.amazonaws.com/272658_ae4d482c86514674be17042c852ebbfc.html)

cat("model
    {

    for ( i in 1:N ) {
    
    P[i] <- 1/V[i]
    
    y[i] ~ dnorm( d, P[i] )

    }

    ### Define the priors
    d ~ dnorm( 0, 0.00001 )

    ### Transform the ln(OR) to OR
    OR <- exp( d )

    }", file="aspirinFE.txt")
```

```{r}
#### Set up the JAGS model and settings
jags.m <- jags.model( file = "aspirinFE.txt", data=dat, inits=inits, n.chains=1, n.adapt=500 )
```
```{r}
params <- c("d", "OR")

## run JAGS and save posterior samples
samps <- coda.samples( jags.m, params, n.iter=10000 )
summary(samps)
plot(samps)
```



